\textbf{Honeypot Assignment: \\ \emph{Group Contagiarium}}

### 2012-01-10 Paper_honeypot.tex
Connecties between the attacks uitgewerkt

The attackers using ``ZmEu'' found one valid path: /phpmyadmin/, however he did not exploit this. 
It is interesting to see that both several \emph{''-''} and several ``ZmEu'' users are scanning for ``/w00tw00t.at.blackhats.romanian.anti-sec:)'' and ``/w00tw00t.at.ISC.SANS.DFind:)''

@@

``Morfeus Fucking Scanner'' was used by one attacker, that solely searched for /user/soapCaller.bs. We could not find anything on this .bs file.
\end{itemize}

@@

>>>>

The attackers using ``ZmEu'' found one valid path: /phpmyadmin/, however he did not exploit this. 
It is interesting to see that both several \emph{''-''} and several ``ZmEu'' users are scanning for ``/w00tw00t.at.blackhats.romanian.anti-sec:)'' and ``/w00tw00t.at.ISC.SANS.DFind:)'' These clients are alleged to be for reconnacance purposes.

@@

``Morfeus Fucking Scanner'' was used by one attacker, that solely searched for /user/soapCaller.bs. Multiple sources say this might be a Drupal exploit.
\end{itemize}

@@

Three clients connected to both HTTP and Kippo, which raised our suspision:
\begin{itemize}
\item 58.17.52.14

This citizen of the Peoples Republic of China poked every possible entrance, in two consequental days: he made a connection to Kippo and disconnected immideately. He also requested the main / folder via HTTP, using the client "-". Scanlogd also reported scans on port 80, 8080, 3128, 9415, 8909, 9592, 1080, 443. Unfortunately for us we were not attractive for him to return and actually break in.

\item 61.190.172.2

On four occasions this inhabitant of China probed us, split over 4 weeks. He also just connected to Kippo (Suricata reported a SSH-scan) and disconnected: he did this for fourty times in 3 minutes. Interestingly enough he was one of the users of the Morfius Fucking Scanner client: only requesting the /user/soapCaller.bs file.

\item 125.88.75.199

The last prober was also from China. On November 22th he connected to Kippo to automaticly disconnect again. He also requested the / folder via HTTP with the "-" client. He was only seen at this occasion.
